---
title: "P8105 HW1 jl6046"
author: "Brian Jo Hsuan Lee"
date: 2021-09-25
output: github_document
---

```{r}
library(tidyverse)
```


Create a data frame with 4 varibles and 10 observations

```{r}
set.seed(33)
rand_three = sample.int(n=3, size=10, replace=TRUE)

p1_df = tibble(
  rand_samp = rnorm(10),
  pos_samp = rand_samp > 0,
  len_ten_char = 'laundryday',
  len_ten_fac = factor(rand_three, labels=c("whites", "colors", "delicates"))
)
```

Calculate the means of each variable

```{r}
samp_mean = mean(pull(p1_df, rand_samp))
pos_samp_mean = mean(pull(p1_df, pos_samp))
char_mean = mean(pull(p1_df, len_ten_char))
fac_mean = mean(pull(p1_df, len_ten_fac))
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
