---
title: "P8105 HW1 jl6046"
author: "Brian Jo Hsuan Lee"
date: 2021-09-25
output: github_document
---

Import package 'tidyverse'.

```{r, message=FALSE}
library(tidyverse)
```

Create a data frame with 4 varibles and 10 observations.

```{r}
set.seed(33)
rand_three = sample.int(n=3, size=10, replace=TRUE)

p1_df = tibble(
  rand_samp = rnorm(10),
  pos_samp = rand_samp > 0,
  len_ten_char = 'laundryday',
  len_ten_fac = factor(rand_three, labels=c("whites", "colors", "delicates"))
)

p1_df
```

Calculate the means of each of the 4 variables.

```{r, warning=FALSE}
samp_mean = mean(pull(p1_df, rand_samp))
samp_mean
pos_samp_mean = mean(pull(p1_df, pos_samp))
pos_samp_mean
char_mean = mean(pull(p1_df, len_ten_char))
char_mean
fac_mean = mean(pull(p1_df, len_ten_fac))
fac_mean
```

Only numeric or logical values could be taken the means of. Therefore, means of nominal values, such as characters and factors, are set to 'Not Available'.

We may understand this outcome by converting logical, character and factors into numeric values:

```{r, results='hide', warning=FALSE}
p1_df %>% add_column(pos_samp_num = as.numeric(pull(p1_df, pos_samp))
                     , .after = "pos_samp")
p1_df %>% add_column(char_num = as.numeric(pull(p1_df, len_ten_char))
                     , .after = "len_ten_char")
p1_df %>% add_column(fac_num = as.numeric(pull(p1_df, len_ten_fac)))
```
When logicals are converted to doubles, 'TRUE's' become 1s and 'FALSE's' become 0s, and factors are converted into their assigned indices. Characters, on the other hand, cannot be converted successfully. 

Load 'penguins' data from "palmerpenguins". Check the name and number of variables as well as the number of observations. 

```{r}
data("penguins", package = "palmerpenguins")
p2_df_colnames = colnames(penguins)
p2_df_colnames
p2_df_obs_size = nrow(penguins)
p2_df_obs_size
p2_df_var_size = ncol(penguins)
p2_df_var_size
```

'penguins' is a 344 by 8 table, and we're interested in the average length of penguin flippers documented.

```{r}
flip_mean = mean(pull(penguins, flipper_length_mm), na.rm=TRUE)
flip_mean
```

The mean flipper length is 200.9 mm among the observed samples, ignoring the missing values. 

Show correlation between penguin bill lengths and flipper lengths using a scatter plot.

```{r, warning=FALSE}
scatterplot_df = tibble(
  flip_len = pull(penguins, flipper_length_mm),
  bill_len = pull(penguins, bill_length_mm),
  spec_color = pull(penguins, species)
)

ggplot(scatterplot_df, aes(x=bill_len, y=flip_len, color=spec_color)) + geom_point() + labs(title="The Length Correlation of Bills and Flippers of 3 Penguin Species") + ylab("Flipper Length (mm)") + xlab("Bill Length (mm)") + theme(legend.title = element_blank()) + theme(plot.title = element_text(size=12))
```

Save the scatterplot in the directory as a .png

```{r, warning=FALSE}
ggsave(
  filename = "bill_v_flippers.png", 
  plot = last_plot()
)
```