---
title: "P8105 HW1 jl6046"
author: "Brian Jo Hsuan Lee"
date: 2021-09-25
output: github_document
---

Import package 'tidyverse'.

```{r, message=FALSE}
library(tidyverse)
```

Create a data frame with 4 varibles and 10 observations.

```{r}
set.seed(33)
rand_three = sample.int(n=3, size=10, replace=TRUE)

p1_df = tibble(
  rand_samp = rnorm(10),
  pos_samp = rand_samp > 0,
  len_ten_char = 'laundryday',
  len_ten_fac = factor(rand_three, labels=c("whites", "colors", "delicates"))
)

p1_df
```

Calculate the means of each of the 4 variables.

```{r, warning=FALSE}
samp_mean = mean(pull(p1_df, rand_samp))
samp_mean
pos_samp_mean = mean(pull(p1_df, pos_samp))
pos_samp_mean
char_mean = mean(pull(p1_df, len_ten_char))
char_mean
fac_mean = mean(pull(p1_df, len_ten_fac))
fac_mean
```

Only numeric or logical values could be taken the means of. Therefore, means of nominal values, such as characters and factors, are set to 'Not Available'.

We may understand this outcome by converting logical, character and factors into numeric values:

```{r, results='hide', warning=FALSE}
p1_df %>% add_column(pos_samp_num = as.numeric(pull(p1_df, pos_samp))
                     , .after = "pos_samp")
p1_df %>% add_column(char_num = as.numeric(pull(p1_df, len_ten_char))
                     , .after = "len_ten_char")
p1_df %>% add_column(fac_num = as.numeric(pull(p1_df, len_ten_fac)))
```
When logicals are converted to doubles, 'TRUE's' become 1s and 'FALSE's' become 0s, and factors are converted into their assigned indices. Characters, on the other hand, cannot be converted successfully. 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
